---
title: My dynamic report
output: html_fragment
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, error=FALSE)

```

```{css}
body {
  background-color: #FEE7D8;
  padding: 25px;
  font-size: 16px;
  font-weight: bold;
  color:#3e1f25;
  font-style: oblique;
  }

p {
 color:#3e1f25;
 font-style: oblique;
}

h2 {
  font-weight: bold;
  font-size: 35px
}

h3 {
  font-size: 23px
  font-weight: bold
}
```

## Recent alcoholic beverage consumption patterns observed at a restaurant in Auckland


The data discussed in this dynamic report is a collection of continuous observational data, logged over time on Google Forms.

The form was designed to help with identifying patterns of alcohol consumption depending on each day, day of the week, and generation.

The data was collected based on first-hand observations as well as observations made upon reading reports made to the surveyor.
The data was collected over time, and logged together separately.


Below are some of the summary values from the data collected,
as well as plots to aid visualising the data:

\n
\n


```{r}

library(tidyverse)

logged_data <- read_csv("https://docs.google.com/spreadsheets/d/e/2PACX-1vTzFh1d53cXi4FXccTIkY17Uh46c2NzeDJVnRCsmd3VdWNAWLU9rsblcIdn1TytJWWqWnkiZ75JInbx/pub?gid=2036014978&single=true&output=csv")


#Renaming variables for coding
latest_data <- logged_data[2:6] %>%
  rename(day_of_week = 1,
         virgin_drinks = 2,
         younger_drink = 3,
         older_drink = 4,
         nodrink_reason = 5)

glimpse(latest_data)

virgin_drinks_vector = latest_data$virgin_drinks

#Summary stats on raw data
num_obs <- length(virgin_drinks_vector)
min_virgin_drinks <- min(virgin_drinks_vector)
max_virgin_drinks <- max(virgin_drinks_vector)
mean_virgin_drinks <- mean(virgin_drinks_vector) %>%
  round(1)

paste("The minimum percentage of non-alcoholic beverages consumed by guests in March was", min_virgin_drinks, "%.")

paste("The maximum percentage of non-alcoholic beverages consumed by guests in March was", max_virgin_drinks, "%.")

paste("The average percentage of non-alcoholic beverages consumed by guests in March was", mean_virgin_drinks, "%.")


#Average of non-alcoholic beverage percentages for weekends
weekend_dates <- c(1,2,7,8,9,14,15,16,21,22,23,28,29,30)
virgin_drinks_weekend <- virgin_drinks_vector[weekend_dates]
mean_weekend <- mean(virgin_drinks_weekend) %>%
  round(1)

paste("The average percentage of non-alcoholic beverages consumed by guests on weekends in March was", mean_weekend, "%.")

#Average of non-alcoholic beverage percentages for weekdays
virgin_drinks_weekday <- virgin_drinks_vector[c(3,4,5,6,10,11,12,13,17,18,19,20,24,25,26,27,31)]
mean_weekday <- mean(virgin_drinks_weekday) %>%
  round(1)

paste("The average percentage of non-alcoholic beverages consumed by guests on weekends in March was", mean_weekday, "%.")

#reordering variable day_of_week to be ordered with the calendar instead of alphabetically.
latest_data$day_of_week <- factor(latest_data$day_of_week, levels = c("Monday", "Tuesday", "Wednesday", "Thursday", "Friday", "Saturday", "Sunday"))


#Bar charts for dynamic report
ggplot(data = latest_data) +
  geom_bar(aes(x = younger_drink)) +
    labs(title = "Have the majority of younger guests consumed alcohol today?",
       subtitle = "Younger guests are whom are noted or appear to be younger than 30.")

ggplot(data = latest_data) +
  geom_bar(aes(x = older_drink)) +
    labs(title = "Have the majority of older guests consumed alcohol today?",
       subtitle = "Younger guests are whom are noted or appear to be older than 30.")

ggplot(data = latest_data) +
  geom_bar(aes(x = nodrink_reason)) +
    labs(title = "For the people who weren't drinking - what were the perceived reasons?")

#box plots devised for insight on potential interaction between variables
ggplot(data = latest_data) +
  geom_boxplot(aes(y = virgin_drinks, x = day_of_week)) +
    labs(title = "Percentages of beverages non-alcoholic beverages sold",
         subtitle = "for each days of the week in March")

ggplot(data = latest_data) +
  geom_boxplot(aes(y = virgin_drinks, x = younger_drink)) +
      labs(title = "Percentages of non-alcoholic beverages sold",
      subtitle = "vs whether younger guests were drinking")




```
\n
\n

## Inferences
\n
\n

We can observe the following from the data above:
\n

- Majority of younger guests at the restaurant did not consume alcohol for almost half of the days in March

- Majority of older guests at the restaurant consumed alcohol on every day of March.

- For those who did not drink, the primary reason as observed was personal preference.

- During the weekends, the percentages of non-alcoholic beverages sold is notably lower.

- During weekdays, much more non-alcoholic beverages are sold. However, it appears to fluctuate on each given day.





